Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-09 paper.tex
minor change for manuscript

All results calculated for this paper were the result of \emph{ab initio}
simulations carried out using plane-wave Density Functional Theory
package VASP \cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the
Projector Augmented Wave (PAW) approach with Kresse’s mainly GW
Pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
calculated using the Hybrid functional HSE06, with Spin Orbit Coupling
explicitly included. The geometries were converged both in cell
parameters and ionic positions, with forces below 0.04 eV/Å. A vacuum
spacing of at least 12 Å was used for each material. A K-Point grid of
\(7\times7\times1\) was used to relax, with an initial relaxation
carried out at PBE level and a subsequent relaxation carried out at
HSE06 level, allowing both cell parameters and ionic positions to
relax each time. In VASP, the tag PREC=High was used, giving a plane
wave kinetic energy cutoff of 30\% greater than the highest given in
the pseudopotentials used in each material, guaranteeing that absolute
energies were converged to a few meV and the stress tensor to within a
few kBar. A final HSE06 calculation with SOC was then carried out
using a 14x14x1 K-Point grid, from which the density of states was
taken.
\todo{add more notes here}

>>>>

All results calculated for this paper were the result of \emph{ab
  initio} simulations carried out using plane-wave Density Functional
Theory (DFT) package VASP
\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the Projector
Augmented Wave (PAW) approach with Kresse’s mainly GW
Pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
\cite{Heyd_2003,HSE_2006}, with Spin Orbit Coupling (SOC) explicitly
included. The geometries were converged both in cell parameters and
ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA is
used. A k-point grid of \(7\times7\times1\) was used to relax the
superlattice, with an initial relaxation carried out at the
Perdew-Burke-Ernzerhof
(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
exchange-correlation functional level and a subsequent relaxation
carried out at HSE06 level, allowing both cell parameters and ionic
positions to relax each time. In VASP, the tag PREC=High was used,
giving a plane wave kinetic energy cutoff of 30\% greater than the
highest given in the pseudopotentials used in each material,
guaranteeing that absolute energies were converged to a few meV and
the stress tensor to within a few kBar.  Calculation of the
macroscopic ion-clamped dielectric tensor were carried out with an
18$\times$18$\times$1 k-grid and electric field strength of 0.001
eV/\AA. Bulk layered materials were constructed by relaxing the c-axis
length of corresponding monolayer material with the interlayer van der
Waals (vdW) interactions calculated by non-local vdW correlation
functional\cite{Lee_2010_vdFD2}. The dielectric properties of bulk
layered materials were calculated at PBE level with
18$\times$18$\time$6 k-grid with same parameter as for monolayer.
